Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Added paragraphs in threats to validty.
Added paragraphs to differentiate different threats more clearly.

%-------------------------------
\subsection{Threats to validity}
%-------------------------------
We report an assessment of both our approaches over a diverse set of real-world benchmarks. Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks. 
%
Our algorithm to select suitable FWL word widths to model the plant behavior employs a heuristic based on user-provided controller word-width specifications. For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis. This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high. 
%
The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.

>>>>

%-------------------------------
\subsection{Threats to validity}
%-------------------------------
\textit{Benchmark selection:} We report an assessment of both our approaches over a diverse set of real-world benchmarks. Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.\\ 
%
\textit{Plant precision and discretization heuristic:} Our algorithm to select suitable FWL word widths to model the plant behavior employs a heuristic based on user-provided controller word-width specifications. For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis. This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.\\ 
%
\textit{Abstraction on other properties:} The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.
